Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-25 manuscript/ERL_global_C_review.Rmd
Update ERL_global_C_review.Rmd

#Table 1 for this manuscript
T1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
n_records <- sum(T1[,"records"])

#ForC raw
ForC_measurements <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_measurements.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_records_age_unk <- sum(is.na(as.numeric(ForC_measurements[, "stand.age"])))  #total n records no age info
ForC_plots <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_plots.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_sites <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_sites_coord_unk <- sum(is.na(as.numeric(ForC_sites[, "lat"])))  #total n records no geographic coordinates
  n_areas <- max(ForC_sites[,"geographic.area"], na.rm = TRUE )

@@

#total numbers of plots and areas (all variables combined)
n_plots_tot <- NA
n_areas_tot <- NA

# percent eligible for inclusion in analysis

n_focal_variable_records_eligible_for_inclusion <- NA #This is prior to assigning biome groupings

# records by biome grouping
n_records_BoB <- NA
n_records_Bomixed <- NA
n_records_Te_mixed <- NA

@@

This review synthesizes data from the ForC database [Fig. 1; https://github.com/forc-db/ForC; @anderson-teixeira_carbon_2016, @anderson-teixeira_forc_2018]. 
ForC amalgamates numerous intermediary data sets (*e.g.*, REFS) and original studies. 
Original publications were referenced to check values and obtain information not contained in intermediary data sets, although this process has not been completed for all records. 
The database was developed with goals of understanding how C cycling in forests varies across broad geographic scales and as a function of stand age. 
As such, there has been a focus on incorporating data from regrowth forests (*e.g.*, Anderson et al 2006, Martin et al 2013, Bonner et al 2013) and obtaining stand age data when possible [83% of records in v.2.0; @anderson-teixeira_forc_2018]. 
Particular attention was given to developing the database for tropical forests [@anderson-teixeira_carbon_2016], yet these represented only approximately one-third of records in ForC v.2.0 [@anderson-teixeira_forc_2018]. 
Since publication of ForC v.2.0, we added the following data to ForC: the Global Database of Soil Respiration Database [SRDB v.##; @bond-lamberty_global_2010], the Global Reforestation Opportunity Assessment database [GROA v1.0; @cook-patton_mapping_2020; @anderson-teixeira_forc-dbgroa_2020], and data from several publications [e.g., @taylor_temperature_2017, @lutz_global_2018, @johnson_climate_2018; detailed list at https://github.com/forc-db/ForC/blob/master/database_management_records/ForC_data_additions_log.csv]. 
We note that there remains a significant amount of relevant data that is not yet included in ForC, particularly biomass data from national forest inventories (*e.g.*,: REFS). 
The database version used for this analysis has been tagged as a new release on Github (XX) and assigned a DOI through Zenodo (DOI: TBD).

@@

Data were analyzed to produce basic summaries of C cycle patterns across biomes and stand ages. **(this par & following are confusing/ incomplete--needs work)**
For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot. 
Values were then averaged across plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records. 
This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC. 
Finally, for figures 6 and 7, the original values were analyzed via a linear mixed effects model ('lmer' function in 'lme4' R package) with biome as fixed effect and plot nested within geographic.area as random effects on the intercept. 
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another. There were enough data to run this analysis for all focal variables but $DW_{down}$.

For young (<100yrs) forest types, we employed a mixed effects model with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect on the intercept. 
When the effect of stand.age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome - stand.age interaction was included in the model. 
In the C cycle schematics for young forests, we report equations based on these models. 
In cases where there was no significant effect of stand.age, records were averaged as for mature stands.

>>>>

#ForC raw
ForC_measurements <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_measurements.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_records_age_unk <- sum(is.na(as.numeric(ForC_measurements[, "stand.age"])))  #total n records no age info
  n_SRDB=NA
  n_GROA=NA
ForC_plots <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_plots.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_sites <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_sites_coord_unk <- sum(is.na(as.numeric(ForC_sites[, "lat"])))  #total n records no geographic coordinates
  n_areas <- max(ForC_sites[,"geographic.area"], na.rm = TRUE )

@@

# limiting to variables and biomes of interest:
n_focal_variable_records_eligible_for_inclusion <- NA # records_eligible_for_inclusion, limited to focal variables

# records for excluded biome groupings ? 
n_records_BoB <- NA
n_records_Bomixed <- NA
n_records_Te_mixed <- NA

#Records included in the analysis
T1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
  n_records <- sum(T1[,"records"])

n_plots_tot <- NA #total numbers of plots used in the analysis (all variables combined)
n_areas_tot <- NA #total numbers of areas used in the analysis (all variables combined)

@@

This review synthesizes data from the ForC database [Fig. 1; https://github.com/forc-db/ForC; @anderson-teixeira_carbon_2016, @anderson-teixeira_forc_2018]. 
ForC amalgamates numerous intermediary data sets (*e.g.*, REFS) and original studies. 
Original publications were referenced to check values and obtain information not contained in intermediary data sets, although this process has not been completed for all records. 
The database was developed with goals of understanding how C cycling in forests varies across broad geographic scales and as a function of stand age. 
As such, there has been a focus on incorporating data from regrowth forests (*e.g.*, Anderson et al 2006, Martin et al 2013, Bonner et al 2013) and obtaining stand age data when possible [83% of records in v.2.0; @anderson-teixeira_forc_2018]. 
Particular attention was given to developing the database for tropical forests [@anderson-teixeira_carbon_2016], yet these represented only approximately one-third of records in ForC v.2.0 [@anderson-teixeira_forc_2018]. 
Since publication of ForC v.2.0, we added the following data to ForC: the Global Database of Soil Respiration Database [SRDB v.##, `r n_SRDB` records; @bond-lamberty_global_2010], the Global Reforestation Opportunity Assessment database [GROA v1.0, `r n_GROA` records; @cook-patton_mapping_2020; @anderson-teixeira_forc-dbgroa_2020], and data from several publications [e.g., @taylor_temperature_2017, @lutz_global_2018, @johnson_climate_2018; detailed list at https://github.com/forc-db/ForC/blob/master/database_management_records/ForC_data_additions_log.csv]. 
We note that there remains a significant amount of relevant data that is not yet included in ForC, particularly biomass data from national forest inventories (*e.g.*,: REFS). 
The database version used for this analysis has been tagged as a new release on Github (XX) and assigned a DOI through Zenodo (DOI: TBD).

@@

Data were analyzed to produce ...
*Schematics:* 
Data were summarized to produce schematics of C cycling across the eight biome - age group combinations identified above.
For mature forests, to obtain the values reported in the C cycle schematics, we first averaged any repeated measurements within a plot. 
Values were then averaged across plots clustered within 25 km of one another [*sensu* @anderson-teixeira_forc_2018], weighting by area sampled if available for all records. 
This step was taken to avoid pseudo-replication and to combine any records from sites with more than one name in ForC.

*FIgs 6-7*
Finally, for figures 6 and 7, the original values were analyzed via a linear mixed effects model ('lmer' function in 'lme4' R package) with biome as fixed effect and plot nested within geographic.area as random effects on the intercept. 
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another. There were enough data to run this analysis for all focal variables but $DW_{down}$.

For young (<100yrs) forest types, we employed a mixed effects model with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect on the intercept. 
When the effect of stand.age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome - stand.age interaction was included in the model.
